Malacology: A Programmable Storage System

### 2017-03-08 paper/6_evaluation.tex
paper: tweaks
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[tbp]
\centering
\includegraphics[width=60mm,trim={1 4 4 1.3cm},clip]{figures/iface-update-delay.pdf}
\caption{
[\href{https://github.com/michaelsevilla/malacology-popper/tree/v2.1/experiments/mon-paxos-update/viz.py}{source}]
Cluster-wide interface update latency, excluding the Paxos proposal cost for
interface commit.}
\label{fig:propdelay}
\end{figure}

>>>>

\begin{figure}[tbp]
\centering
\includegraphics[width=60mm,trim={1 4 4 1.3cm},clip]{figures/iface-update-delay.pdf}
\caption{
[\href{https://github.com/michaelsevilla/malacology-popper/tree/v2.1/experiments/mon-paxos-update/viz.py}{source}]
Cluster-wide interface update latency, excluding the Paxos proposal cost for
committing the Service Metadata interface.}
\label{fig:propdelay}
\end{figure}

### 2017-03-08 paper/9_conclusion.tex
paper: tweaks
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

We thank the EuroSys reviewers for their hard work, attentiveness, and
genuinely helpful suggestions. We also thank Mahesh Balakrishnan for
championing and shepherding the paper. This work was partially funded by the
Center for Research in Open Source
Software\footnote{\url{http://cross.ucsc.edu}}, the DOE Award
DE-SC0016074, and the NSF Award 1450488.

\textbf{Note}: this paper follows The Popper
Convention~\cite{jimenez_popper_2016}. The Popper
Convention\footnote{\url{http://falsifiable.us}} is equivalent to
the ACM's Result and Artifiact Review and Badging procedures.
\includegraphics[width=3.5mm]{figures/popper.png}

>>>>

We thank the EuroSys reviewers for their hard work, attentiveness, and
genuinely helpful suggestions. We especially thank Mahesh Balakrishnan for
championing and shepherding the paper. This work was partially funded by the
Center for Research in Open Source
Software\footnote{\url{http://cross.ucsc.edu}}, the DOE Award
DE-SC0016074, and the NSF Award 1450488.

\textbf{Note}: this paper follows The Popper
Convention~\cite{jimenez_popper_2016}. The Popper
Convention\footnote{\url{http://falsifiable.us}} is equivalent to
the ACM's Result and Artifact Review and Badging procedures.
\includegraphics[width=3.5mm]{figures/popper.png}
